%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Nmx Global Software} % Organization
    {Islamabad, Pakistan} % Location
    {Jan. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provisioned an easily managable Front/UI infrastructure utilizing Ui libraries like Material UI, React‑Bootstrap, Sass both in Typescript and
        Javascript.}
        \item {Architected and implemented dashboards to give members a more comprehensive insight into their working.}
        \item {Writing React components and managing Dataflow within the application using Redux actionbased architecture.}
        \item {Implemented several API microservices in Node.js, Python making use of ORM,s in the server enviroment.}
        \item {Worked and Improved an OpenSource Project (Limesurvey).Fixed bugs along with the development of required features on pre‑existing functionality.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Python Developer} % Job title
    {} % Organization
    {} % Location
    {Jan. 2016 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and deployed automation bots utilizing selenium focusing on ease of use, flexibility, and scaling.}
        \item {Developed efficient web-crawlers for data extraction from various websites using lxml and BeautifulSoup for analysis.}
        \item {Implemented RESTful API server using Swagger UI for communcation between frontend and the backend. }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
