%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Core Developer} % Affiliation/role
    {Neural Edge (Nmx Global Software)} % Organization/group
    {React/Redux, Flask, SQLalchemy, PostgreSQL} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A Cloud service for Intelligent Decision making for various corporate clients.Developed in React/Redux for Front and Flask for Backend.}
        \item {Implemented application interaction with server side using JSON parsing.Performed Database ORM Query Optimizations.}
        \item {Worked  extensively with React UI Framework,UI Navigation View, UI Table View, UI Tab Bar Controller , UI Collection View and Storyboard.}
        \item {Participated in daily Scrums and monthly Sprint planning.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {FRONT-END DEVELOPER} % Affiliation/role
    {Heartbeat (Schell Brothers)} % Organization/group
    {Node.js, Appollo GraphQL, React, React‑Bootstrap} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A Saas(Software as a Service) CRM application that is capable of handling more than 10000 users simultaneously.}
        \item {Developed dashboards for different types of users, CRUD interfaces along‑with data queries using Appollo GraphQL.}
        \item {Coordinating with QA for fixing the issues generated by QA Team.}
        \item {Applied Latest React Techniques such as memoization for quicker application response to users.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {FRONT‑END DEVELOPER} % Affiliation/role
    {Cloud Pro (Nmx Global Software)} % Organization/group
    {React/TypeScript, MongoDB, FeathersJs} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A Cloud application built in React/Typescript for maintainence and provision of Cloud Services to numerous clients.}
        \item {To maintain the existing code base to standards determined by the Project Manager, by performing optimizations and reworks.}
        \item {Assist in the development and creation of new application team initiatives.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CORE PROJECT MEMBER} % Affiliation/role
    {COMSATS (Final Year Projects, Career Expo Comsats)} % Organization/group
    {Python, TensorFlow, Kivy Framework, Rasberry Pi} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed in python using Kivy Framework for Cross Platform UI development along with TensorFlow Framework for Model Training ,Optimization and testing.}
        \item {It performed monitoring and analysis on a set of Image frames.A Vision‑Based Security system.It relied on 3 layers of security which are human detection, Face detection and Gait detection.}
        \item {Gait detection was applied using Recurrent neural networks.Made use of Transfer Learning Technique for our Deep learning Model.}
        \item {Awarded 2nd Position in Open House Competition held in Comsats University Islamabad.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CORE DEVELOPER} % Affiliation/role
    {ReactJS Resume Template (Portfolio Project)} % Organization/group
    {ReactJs, SASS, HTML,Github Pages} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Redesigned and Converted a pure HTML based Template developed by Themezy into ReactJs for Personal Portfolios.}
        \item {Made use of JSON based Data storing architecture to generate UI/UX interfaces for interaction.}
        \item {Adhered to latest Frameworks standards within the Code base.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
